### 2016-10-24 R/ITHIM.Rmd
TRVLCMIN -> TRVL_MIN

NHTS.trips <- with(DAYV2PUB,{
    data.frame(HOUSEID = HOUSEID,
                   PERSONID = PERSONID,
                   TDCASEID = TDCASEID,
                   AT = ifelse(TRPTRANS == "22", "cycle",
                        ifelse(TRPTRANS == "23", "walk",
                        ifelse(!is.na(TRPTRANS), "other", NA))),
                   TRVL_MIN = as.numeric(TRVL_MIN),
                   TRVLCMIN = ifelse(as.numeric(TRVLCMIN) != 0, as.numeric(TRVLCMIN), NA),
                   URBRUR  = as.factor(URBRUR),
                   MSACAT = as.factor(MSACAT),
                   MSA = ifelse(MSASIZE %in% 1:5, TRUE, FALSE),
                   TRPTRANS = as.factor(TRPTRANS),
                   TRPMILES = as.numeric(TRPMILES)
)})

@@

```{r summary, fig.width = 20, fig.height = 10, eval = compute, echo = FALSE, message = FALSE, warning = FALSE}
walkHours <- with(subset(NHTS.trips, {
    AT == "walk" & TRPMILES < 10 & TRPMILES/TRVL_MIN*60 < 8 & TRVL_MIN > 5 #& TRPMILES/TRVL_MIN*60 > 0.5
}), TRVL_MIN/60)

walkMiles <- with(subset(NHTS.trips, {
    AT == "walk" & TRPMILES < 10 & TRPMILES/TRVL_MIN*60 < 8 & TRVL_MIN > 5 #& TRPMILES/TRVL_MIN*60 > 0.5
}), TRPMILES)

cycleHours <- with(subset(NHTS.trips, {
      AT == "cycle" & TRPMILES < 25 & TRPMILES/TRVL_MIN*60 < 25 & TRVL_MIN > 5 #& TRPMILES/TRVL_MIN*60 > 1
}), TRVL_MIN/60)

cycleMiles <- with(subset(NHTS.trips, {
      AT == "cycle" & TRPMILES < 25 & TRPMILES/TRVL_MIN*60 < 25 & TRVL_MIN > 5 #& TRPMILES/TRVL_MIN*60 > 1
}), TRPMILES)

walkSpeed <- median(walkMiles/walkHours, na.rm = TRUE)
cycleSpeed <- median(cycleMiles/cycleHours, na.rm = TRUE)

Dwalk <- data.frame(Hours = walkHours, Miles = walkMiles, Speed = walkMiles/walkHours, mode = "walk")
Dcycle <- data.frame(Hours = cycleHours, Miles = cycleMiles, Speed = cycleMiles/cycleHours, mode = "cycle")

D <- rbind(Dwalk,Dcycle)

Dspeed <- data.frame(speed = c(1,1), intercept = log10(c(walkSpeed,cycleSpeed)), mode = c("walk","cycle"))

g <- ggplot(D, aes(Hours, Miles, colour = mode)) + geom_point()
g <- g + geom_abline(aes(slope = speed, intercept = intercept, colour = mode), Dspeed) + facet_grid(. ~ mode)
g + scale_y_log10() + scale_x_log10() + theme_bw()

g <- ggplot(D, aes(Speed, ..density.., fill = mode)) + geom_histogram() + theme_bw() + scale_x_continuous(name="Speed") + scale_y_continuous(name="Density") + facet_grid(. ~ mode, scales = "free")
g

@@

```{r subset, eval = compute, fig.width = 10, echo = FALSE}
NHTS.person <- subset( NHTS.person, MSA == TRUE )
NHTS.trips <- subset(NHTS.trips, !is.na(TRPMILES))

NHTS <- merge(NHTS.person, NHTS.trips, by = c("HOUSEID","PERSONID"), all.x = TRUE)
NHTS <- within(NHTS, TRPMILES <- ifelse(is.na(TRPMILES), 0, TRPMILES))
saveRDS(NHTS, file = "./data/NHTS.rds")
```

>>>>

NHTS.trips <- with(DAYV2PUB,{
    data.frame(HOUSEID = HOUSEID,
                   PERSONID = PERSONID,
                   TDCASEID = TDCASEID,
                   AT = ifelse(TRPTRANS == "22", "cycle",
                        ifelse(TRPTRANS == "23", "walk",
                        ifelse(!is.na(TRPTRANS), "other", NA))),
                   TRVL_MIN = as.numeric(TRVL_MIN),
                   #TRVLCMIN = as.numeric(TRVLCMIN),
                   URBRUR  = as.factor(URBRUR),
                   MSACAT = as.factor(MSACAT),
                   MSA = ifelse(MSASIZE %in% 1:5, TRUE, FALSE),
                   TRPTRANS = as.factor(TRPTRANS),
                   TRPMILES = as.numeric(TRPMILES)
)})

@@

@@

```{r subset, eval = compute, fig.width = 10, echo = FALSE}
NHTS.person <- subset( NHTS.person, MSA == TRUE )
NHTS.trips <- subset(NHTS.trips, !is.na(TRVL_MIN))

NHTS <- merge(NHTS.person, NHTS.trips, by = c("HOUSEID","PERSONID"), all.x = TRUE)
NHTS <- within(NHTS, TRVL_MIN <- ifelse(is.na(TRVL_MIN), 0, TRVL_MIN))
saveRDS(NHTS, file = "./data/NHTS.rds")
```

### 2016-10-24 R/appendix.Rmd
TRVLCMIN -> TRVL_MIN

>>>>

```{r summary, fig.width = 20, fig.height = 10, eval = compute, echo = FALSE, message = FALSE, warning = FALSE}
walkHours <- with(subset(NHTS.trips, {
    AT == "walk" & TRPMILES < 10 & TRPMILES/TRVL_MIN*60 < 8 & TRVL_MIN > 5 #& TRPMILES/TRVL_MIN*60 > 0.5
}), TRVL_MIN/60)

walkMiles <- with(subset(NHTS.trips, {
    AT == "walk" & TRPMILES < 10 & TRPMILES/TRVL_MIN*60 < 8 & TRVL_MIN > 5 #& TRPMILES/TRVL_MIN*60 > 0.5
}), TRPMILES)

cycleHours <- with(subset(NHTS.trips, {
      AT == "cycle" & TRPMILES < 25 & TRPMILES/TRVL_MIN*60 < 25 & TRVL_MIN > 5 #& TRPMILES/TRVL_MIN*60 > 1
}), TRVL_MIN/60)

cycleMiles <- with(subset(NHTS.trips, {
      AT == "cycle" & TRPMILES < 25 & TRPMILES/TRVL_MIN*60 < 25 & TRVL_MIN > 5 #& TRPMILES/TRVL_MIN*60 > 1
}), TRPMILES)

walkSpeed <- median(walkMiles/walkHours, na.rm = TRUE)
cycleSpeed <- median(cycleMiles/cycleHours, na.rm = TRUE)

Dwalk <- data.frame(Hours = walkHours, Miles = walkMiles, Speed = walkMiles/walkHours, mode = "walk")
Dcycle <- data.frame(Hours = cycleHours, Miles = cycleMiles, Speed = cycleMiles/cycleHours, mode = "cycle")

D <- rbind(Dwalk,Dcycle)

Dspeed <- data.frame(speed = c(1,1), intercept = log10(c(walkSpeed,cycleSpeed)), mode = c("walk","cycle"))

g <- ggplot(D, aes(Hours, Miles, colour = mode)) + geom_point()
g <- g + geom_abline(aes(slope = speed, intercept = intercept, colour = mode), Dspeed) + facet_grid(. ~ mode)
g + scale_y_log10() + scale_x_log10() + theme_bw()

g <- ggplot(D, aes(Speed, ..density.., fill = mode)) + geom_histogram() + theme_bw() + scale_x_continuous(name="Speed") + scale_y_continuous(name="Density") + facet_grid(. ~ mode, scales = "free")
g
